Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-04-04 main.tex
:pencil: Update manuscript

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[acronym]{glossaries-extra}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
% \usepackage[subtle]{savetrees}
% \usepackage{stmaryrd}

@@

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
	#1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}

@@

\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

\begin{document}
	\title{Backscatter Modulation Design for Symbiotic Radio Networks}
	\maketitle

	\begin{section}{Backscatter Model}
		\begin{subsection}{Backscatter Principles}

@@

				\subfloat[Block diagram of a passive tag]{

@@

								to[short] ++(-1,0)
								to[short] ++(0,0.75) node[bareantenna](A){Ant};

@@

					\label{fi:block_diagram_of_a_passive_tag}

@@

				\subfloat[Backscatter modualtion]{

@@

							\draw (WR.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_m$};
							\draw (WR.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_m$};

@@

								to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-2)

@@

					\label{fi:backscatter_modualtion}

@@

			A bistatic backscatter system consists of an excitation source, multiple (semi-)passive tags, and a backscatter reader. When illuminated, the tags simultaneously harvest energy, backscatter message, and demodulate the source signal if necessary. Fig.~\subref*{fi:block_diagram_of_a_passive_tag} shows a typical passive with a scattering antenna, an energy harvester, an integrated receiver\footnote{For example, \cite{Kim2021a} prototyped a compact-size pulse position demodulator based on an envelope detector, which brings great potential to coordination, synchronization, and reflection pattern control.}, a load-switching modulator, and on-chip components (e.g., micro-controller, memory, and sensors). A portion of the impinging signal is absorbed by the tag while the remaining is backscattered to the space. According to Green's decomposition \cite{Hansen1989}, the backscattered signal can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and depends on the antenna geometry and material properties\footnote{The structural mode component can be regarded as part of the environment multipath and modeled by channel estimation \cite{Boyer2014}.}, while the latter is adjustable and depends on the mismatch of the antenna and load impedance. Fig.~\subref*{fi:backscatter_modualtion} illustrates a simplified circuit and backscatter model at tag state $m$. The corresponding reflection coefficient is defined as\footnote{We assume the linear backscatter model where the reflection coefficient is irrelevant to the incident electromagnetic field at the tag \cite{Dobkin2012}.}

@@

		\end{subsection}

		\begin{subsection}{Backscatter Modulation}
			Backscatter modulation is achieved by switching the tag load impedance between different states. For an $M$-ary \gls{qam} at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$, the reflection coefficient $\Gamma_m$ maps to the signal constellation point $\bar{c}_m$ as \cite{Thomas2012a}
			\begin{equation}
				\Gamma_m = \alpha \frac{\bar{c}_m}{\max_{m'} \lvert \bar{c}_{m'} \rvert},
				\label{eq:backscatter_modulation}
			\end{equation}
			where $\alpha \in [0,1]$ is the reflection efficiency at a given direction. For simplicity, we consider an $M$-ary \gls{psk} with constellation set $\mathcal{C} \triangleq \{\bar{c}_1,\ldots,\bar{c}_M\}$, where the $m$-th constellation point is
			\begin{equation}
				\bar{c}_m = \exp \left(j \frac{2 \pi m}{M}\right).
				\label{eq:mpsk}
			\end{equation}

			\begin{remark}
				For passive tags, the reflection efficiency $\alpha$ controls the tradeoff between the harvestable power and backscatter strength: $\alpha = 0$ corresponds to maximum power transfer to the tag, while $\alpha = 1$ with $M$-\gls{psk} corresponds to ideal \gls{irs} with $M$ discrete states.
			\end{remark}
		\end{subsection}
	\end{section}

	\begin{section}{Backscatter Detection and Achievable Rates}
		\begin{subsection}{System Model}
			\begin{figure}[!t]
				\centering
				\def\svgwidth{0.9\columnwidth}
				\import{assets/}{symbiotic_radio.eps_tex}
				\caption{A single-user multi-tag symbiotic radio system.}
				\label{fi:symbiotic_radio}
			\end{figure}
			As shown in Fig.~\ref{fi:symbiotic_radio}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems. In the primary downlink system, the \gls{ap} transmits information to the single-antenna user. In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user serves as the multi-tag backscatter reader. Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and the cascaded forward-backward channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$. For simplicity, we consider a quasi-static block fading model where the channel coefficients remain constant within each coherence interval and vary independently over different coherence intervals, and assume the coherence interval $T$ is much longer than the backscatter symbol period $T_c$ and primary symbol period $T_s$. We also assume the direct channel and all cascaded channels can be successfully estimated and fed back to the \gls{ap}.\footnote{Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging. One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.} Since the tags need to physically switch the loads for backscatter modulation, they communicate at a much longer symbol period (and lower rates) than the primary system. As such, we assume the transitions of all tags are perfectly synchronized, and the backscatter symbol period satisfies $T_c = N T_s$ where $N \gg 1$ is a positive integer.

			Without loss of generality, we focus on the transmissions and detections during one particular backscatter symbol period. To provide a preliminary insight, we assume the primary symbol $s[n]$ at block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is in standard \gls{cscg} distribution, and the backscatter symbol $c_k$ of tag $k$ employs $M$-\gls{psk} modulation by \eqref{eq:mpsk}, i.e., $c_k \in \mathcal{C}$, $\forall k \in \mathcal{K}$. Thus, the signal received by the user at block $n$ can be expressed as\footnote{We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.}
			\begin{equation}
				y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k\right) \boldsymbol{w} s[n] + w[n],
				\label{eq:received_signal}
			\end{equation}
			where $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the active precoder satisfying $\lVert \boldsymbol{w} \rVert^2 \le P$, $P$ is the average transmit power constraint at the \gls{ap}, and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ is the equivalent \gls{awgn} at block $n$. Besides, we collect the backscatter symbols of $K$ tags into $c_{\mathcal{K}} \triangleq \{c_k : k \in \mathcal{K}\}$, stack the received signal over $N$ blocks as $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$, and define the equivalent channel for primary transmission as
			\begin{equation}
				\boldsymbol{h}_{\mathrm{E}}^H(c_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H c_k.
				\label{eq:equivalent_primary_channel}
			\end{equation}

			\begin{remark}
				The proposed symbiotic radio system includes a multiplicative \gls{mac} where the \gls{ap} and the tags simultaneously transmit to the user. It inspired [TODO] to perform \gls{sic} that first non-coherently detects the primary message under backscatter uncertainty, then cancels its contribution and decodes the tag messages. This scheme requires non-coherent coding at the \gls{ap} and $K$ re-encoding, precoding, and subtraction operations at the user. However, different from the conventional \gls{mac} with \gls{sc}, the symbiotic radio system involves \gls{mc} that combines the primary and secondary messages by multiplication. Hence, novel multi-stream detection techniques should be tailored to symbiotic radio systems to accommodate the massive connectivity of tags and the multiplicative combination of links.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Backscatter Detection}
			To reveal the impact of backscatter modulation on the primary transmission and avoid the exponential complexity of joint detection, we extend the non-coherent \gls{ambc} detection \cite{Qian2019} to the multi-tag case, and propose a low-complexity energy detection to decode the backscatter symbols under primary source uncertainty. It requires no dedicated receivers or non-coherent codes at the \gls{ap}, and can be readily implemented over legacy downlink systems.

			\begin{remark}
				One key property of symbiotic radio is the primary message propagates to the user from a known channel and multiple multiplicative channels with uncertainty introduced by backscatter modulation. As such, each reflection coefficient simultaneously encodes the tag message and influences the equivalent channel of the primary link. If the backscatter symbols can be successfully decoded first, they can be modeled within the equivalent channel \eqref{eq:equivalent_primary_channel} as in channel training, instead of being removed by \gls{sic}.
			\end{remark}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
\usepackage{circuitikz}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{fixmath}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pgffor}
\usepackage{pgfgantt}
\usepackage{pgfplots}
\usepackage{physics}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage[acronym]{glossaries-extra}
\usepackage[caption=false,font=footnotesize,subrefformat=parens,labelformat=parens]{subfig}
\usepackage[short]{optidef}
\usepackage[subtle]{savetrees}

@@

\DeclarePairedDelimiterX{\infdivx}[2]{(}{)}{%
	#1\;\delimsize\|\;#2%
}
\newcommand{\infdiv}{D\infdivx}
\renewcommand{\qedsymbol}{\hfill\ensuremath{\Box}}

@@

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

\begin{document}
\title{Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Senior~Member,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{section}{Introduction}
	\IEEEPARstart{B}{ackscatter} is recently re-innovated as a promising approach to support low-power communications and control wireless propagation environments.
	The concept of \gls{ambc} was first proposed in \cite{Liu2013b}, where each tag harvests energy from and modulates information over ambient \gls{rf} signals by periodically switching between different reflection patterns.
	It enables battery-free communication between fully passive nodes, but the backscatter signal strength can be relatively weak and the decoding is subject to strong direct-link interference.
	To solve this, \cite{Yang2018d} exploited the repeating structure of \gls{ofdm} symbol for interference cancellation based on backscatter channel strength.
	Cooperative primary-backscatter decoding using co-located receiver, known as cooperative \gls{ambc}, was proposed in \cite{Yang2018}.
	The authors evaluated the error performance of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, and proposed a low-complexity \gls{ml} detector for frequency-selective fading channels with ambient \gls{ofdm} carrier.
	When transmit cooperation is also available, cooperative \gls{ambc} is more commonly known as \gls{sr} \cite{Liang2020}.
	The authors of \cite{Guo2019b} classified \gls{sr} into commensal, parasitic, and competitive modes based on the relative link priority, then derived their instantaneous achievable rate and optimal power allocation.
	The outage probability for those modes was later studied in \cite{Ding2020}.
	On the other hand, it was concluded in \cite{Long2020a} that if the backscatter symbol period is much longer than the primary symbol period, then the non-coherent achievable rate of primary decoding would approach that of the coherent case.
	The authors also considered the transmit precoder design for weighted sum-rate maximization and transmit power minimization problems.
	\cite{Zhou2019a} explored how the number of transmit antennas, receive antennas, and symbol period ratio asymptotically influence the ergodic rate of primary and backscatter links.
	With multi-antenna at all ends, \cite{Wu2021a} optimized the transmit precoder to maximize the backscatter achievable rate under primary rate constraint.
	However, those paper only considered single tag scenario and the optimal tag multiple access scheme remains unknown.
	\cite{Xu2021a} proposed a \gls{noma}-based \gls{sr} and studied the receive combiner design when the receiver decodes in the order of equivalent channel strength.
	A \gls{tdma}-based \gls{sr} with energy harvesting constraints was also presented in \cite{Yang2021a}, and energy efficiency maximization was considered with respect to transmit power, reflection efficiency, and time allocation design.
	In \cite{Han2021}, random code-assisted backscatter multiple access was combined with \gls{sr}, and the authors evaluated the asymptotic \gls{sinr} performance using random matrix theory.

	On the other hand, \gls{irs} has recently emerged as a promising technique to enhance the energy efficiency.
	In practice, an \gls{irs} consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal (i.e., passive beamforming).
	Different from relay, backscatter and frequency-selective surface \cite{Anwar2018}, \gls{irs} assists the primary transmission using passive components with much lower energy consumption and thermal noise, but is limited to frequency-dependent reflection.
	\cite{Wu2018} proposed an \gls{irs}-assisted \gls{miso} system and jointly optimized the precoder and the phase shifts to minimize the transmit power.
	The active and passive beamforming problem was then extended to the discrete phase shift case \cite{Wu2019a} and the multi-user case \cite{Wu2019}.
	In \cite{Abeywickrama2020}, the authors investigated the impact of non-zero resistance on the reflection pattern and emphasized the coupling between reflection amplitude and phase shift in practice.
	To estimate the cascaded link without \gls{rf}-chains at the \gls{irs}, practical protocols were developed based on element-wise on/off switching \cite{Nadeem2019}, training sequence and reflection pattern design \cite{You2019,Kang2020}, and compressed sensing \cite{Wang2020}.
	\gls{irs} was also added to single-tag and multi-tag \gls{sr} systems to improve backscatter efficiency \cite{Chen2021,Zhang2021d}.
	Recently, the idea of \gls{irs}-empowered \gls{sr} was proposed in \cite{Xu2020b,Hua2022}, where the reflection pattern can be decoupled as the multiplication of whole phase shift matrix and one backscatter symbol.
	The idea was combined with spatial modulation to divide the \gls{irs} into reflection and information and elements, and the error performance of non-coherent backscatter detection was studied accordingly \cite{Hu2021a}.

	To the best of our knowledge, most existing \gls{sr} systems \cite{Yang2018,Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a} assumed Gaussian codebook at the tags and employed \gls{sic} from primary to backscatter link.
	It thus requires non-coherent primary encoding at the transmitter and involves re-encoding, precoding, and subtraction operations that may not be available to legacy receivers.
	Besides, the primary and backscatter symbols in \gls{sr} are mixed by multiplication coding instead of superposition coding, and the backscatter symbol period can be much longer than the primary symbol period due to physical constraints.
	Inspired by above, we propose a novel Metascatter network where multiple battery-free tags ride over a conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{irs}.
	To fully utilize the reflection pattern and signal structure, we also present a novel decoding strategy with minor modifications on existing receivers.
	The contributions of this paper is summarized as follows.

	\emph{First,} Metascatter adapts the input probability distribution of a finite-state backscatter device based on the primary and backscatter \gls{csi}.
	It generalizes the backscatter tags of \gls{sr} and reflecting elements of \gls{irs} to improve the primary-backscatter tradeoff in a flexible manner.
	When the primary link is absolutely prioritized, the tag input probability boils down to \num{1} at the state that maximizes the equivalent channel strength and \num{0} at other states, which is essentially the phase shift selection of an \gls{irs} element.
	When we only care about the backscatter performance, the network boils down to a multi-tag \gls{ambc} and the input design can be simplified accordingly.

	\emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
	When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
	Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.

	\emph{Third,} we characterize the achievable primary-(sum-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

\end{section}

\begin{section}{Backscatter Principles}

@@

		\subfloat[Passive tag structure]{

@@

					to[short] ++(-0.875,0)
					to[short] ++(0,0.5) node[bareantenna](A){Bx};

@@

			\label{fi:passive_tag_structure}

@@

		\subfloat[Equivalent model]{

@@

					\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
					\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};

@@

					to [R=$Z_{\mathrm{A}}$,font=\Large,/tikz/circuitikz/bipoles/length=1cm] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}

@@

			\label{fi:equivalent_model}

@@

	Consider a bistatic backscatter system with an excitation source, multiple (semi-)passive tags, and a backscatter reader.
	The structure of a passive tag is shown in Fig. \subref*{fi:passive_tag_structure}.
	It typically consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}.
	When a tag is illuminated, a portion of the impinging signal is absorbed while the remaining is scattered back, and the tag can harvest energy, transmit message, and decode the source if necessary.
	According to \cite{Hansen1989}, the backscatter signal can be decomposed into a \emph{structural component} that depends on the antenna geometry and material properties, and an \emph{antenna component} that depends on the antenna-load impedance mismatch.
	The former contributes to environment multipath and can be modeled by channel estimation \cite{Boyer2014}, while the latter can be utilized for backscatter modulation.
	As illustrated by Fig. \subref*{fi:equivalent_model}, if $M$ symbol states are available at the tag, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
	\footnote{
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.

@@

	Tags periodically switch between different states to perform backscatter modulation.
	For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in [0,1]$ models the (amplitude) harvest-backscatter efficiency at the direction of interest.
	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{remark}
		By choosing proper load impedance, it is possible to implement any signal constellation or think beyond modulation.
		For example, perfect matching enables maximum power transfer to the tag, while perfect mismatch leads to complete reflection as desired by ideal \gls{irs}.
		It inspires Metascatter to design a smart reflection and unify wireless power transfer, backscatter modulation, and passive beamforming.
	\end{remark}
\end{section}

\begin{section}{Metascatter}
	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{metascatter_system.eps_tex}
			\caption{The proposed Metascatter system.}
			\label{fi:metascatter_system}
		\end{figure}
		As shown in Fig. \ref{fi:metascatter_system}, we propose a single-\gls{ue} multi-\gls{tg} symbiotic radio network where the \gls{rf} signal generated by the $Q$-antenna \gls{ap} is shared by two coexisting systems.
		In the primary point-to-point system, the \gls{ap} transmits information to the single-antenna user.
		In the secondary backscatter system, the \gls{ap} acts as the carrier emitter, the $K$ nearby single-antenna tags modulate their information over the reradiated \gls{rf} signals, and the user receives and decodes the backscatter messages.
		Denote the \gls{ap}-\gls{ue} direct channel as $\boldsymbol{h}_{\mathrm{D}}^H \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-\gls{tg} $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$, the \gls{tg} $k$-\gls{ue} backward channel as $h_{\mathrm{B},k}$, and define the cascaded channel of tag $k$ as $\boldsymbol{h}_{\mathrm{C},k}^H \triangleq h_{\mathrm{B},k} \boldsymbol{h}_{\mathrm{F},k}^H \in \mathbb{C}^{1 \times Q}$.
		For simplicity, we consider a quasi-static block fading model where the channel response remain constant within each coherence interval and vary independently between consecutive blocks.
		Since backscatter modulation involves load switching, tags typically transmit at much lower rate, and we assume the backscatter symbol period is $N \in \mathbb{Z}_{++}$ times the primary symbol period.
		We also assume the direct channel and all cascaded channels can be estimated and fed back to the \gls{ap}.
		\footnote{
			Due to the lack of \gls{rf} chains at the passive tag, accurate and efficient \gls{csi} acquisition at the \gls{ap} can be challenging.
			One possible approach is that the \gls{ap} sends pre-defined pilots, the tags respond in well-designed manners, and the user performs least-square estimation with feedbacks \cite{Bharadia2015,Yang2015b,Guo2019g}.
		}

		Consider the signal model during one backscatter symbol period.
		We assume the primary symbol follows standard \gls{cscg} distribution and the backscatter symbol of all tags employs $M$-\gls{qam}.
		Under perfect synchronization, the signal received by the user at primary symbol block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is
		\footnote{
			We omit the signal reflected by two or more times\cite{Wu2019} and assume the time difference of arrival from different paths are negligible\cite{Guo2019b}.
		}
		\begin{equation}
			y[n] = \left(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k\right) \boldsymbol{w} s[n] + w[n],
			\label{eq:received_signal}
		\end{equation}
		where $\alpha_k$ and $x_k$ denote respectively the harvest-backscatter efficiency and backscatter symbol of tag $k$, $s[n]$ and $w[n] \sim \mathcal{CN}(0,\sigma_w^2)$ denote respectively the primary symbol and \gls{awgn} at block $n$, and $\boldsymbol{w} \in \mathbb{C}^{Q \times 1}$ is the transmit precoder satisfying power constraint $\lVert \boldsymbol{w} \rVert^2 \le P$.
		For the ease of notation, we define $x_{\mathcal{K}} \triangleq \{x_k : k \in \mathcal{K}\}$ as the tag input combination, and $\boldsymbol{y} \triangleq \left[y[1],\ldots,y[N]\right]^T \in \mathbb{C}^{N \times 1}$ as the received signal per backscatter symbol period.
		For primary transmission, the equivalent channel is subject to backscatter modulation uncertainty as
		\begin{equation}
			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_k.
			\label{eq:equivalent_channel}
		\end{equation}

		\begin{remark}
			Metascatter involves an unconventional \gls{mac} where the primary and backscatter symbols of different duration are mixed by \gls{mc} instead of \gls{sc}.
			For each tag, the reflection coefficient not only encodes the backscatter message but also influences the equivalent primary channel \eqref{eq:equivalent_channel}.
			As such, novel receiving strategy other than \gls{sic} should be tailored to signal characteristics to unveil how reflection pattern potentially influences the primary-backscatter tradeoff.
		\end{remark}
	\end{subsection}

	\begin{subsection}{Receiving Strategy}
		We propose a novel receiving strategy where the backscatter symbol of all tags are first jointly identified by non-coherent energy detection, then modeled within equivalent channel \eqref{eq:equivalent_channel} as if passive beamforming.
		Compared with conventional schemes as joint decoding and \gls{sic}, the Metascatter receiver may not achieve as high data rate for one tag, but it avoids non-coherent primary encoding and enables tag multiple access in a practical and low-complexity manner.
		Therefore, we believe it can be compatible to and readily implemented over legacy point-to-point systems.

		Define $m_k \in \mathcal{M}$ as the modulation index of tag $k$, and $m_{\mathcal{K}} \triangleq \{m_k: k \in \mathcal{K}\}$ as the modulation index combination of all tags.
		Recall that $x_k$ and $x_{\mathcal{K}}$ are random variables representing the backscatter symbol of tag $k$ and the symbol combination of all tags, respectively.
		Their instances are denoted by modulation index (combination) as $x_{m_k}$ and $x_{m_\mathcal{K}}$.
		Since any backscatter combination $x_{m_\mathcal{K}}$ remains unchanged over $N$ primary symbol duration, the received signal at symbol block $n$ is only subject to the variation of $s[n]$ and $w[n]$, and follows zero-mean \gls{cscg} distribution with variance
		\begin{equation}
			\sigma_{m_{\mathcal{K}}}^2 = \Bigl\lvert \underbrace{\bigl(\boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \sqrt{\alpha_k} \boldsymbol{h}_{\mathrm{C},k}^H x_{m_k}\bigr)}_{\boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}})} \boldsymbol{w} \Bigr\rvert^2 + \sigma_w^2.
			\label{eq:receive_variance}
		\end{equation}

		Besides, we denote the total received energy as $z \triangleq \lVert \boldsymbol{y} \rVert^2$ and the hypothesis of modulation index combination $m_{\mathcal{K}}$ as $\mathcal{H}_{m_{\mathcal{K}}}$.
		Since $z$ is the sum of $N$ \gls{iid} exponential variables, its conditional \gls{pdf} under $\mathcal{H}_{m_{\mathcal{K}}}$ follows Erlang distribution with shape $N$ and scale $\sigma_{m_{\mathcal{K}}}^2$ as
		\begin{equation}
			f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) = \frac{z^{N-1} e^{-z/\sigma_{m_{\mathcal{K}}}^2}}{\sigma_{m_{\mathcal{K}}}^{2N} (N-1)!}.
			\label{eq:energy_distribution}
		\end{equation}

		Energy-based backscatter detection essentially formulates a discrete-input continuous-output memoryless \gls{mac}.
		To further reduce decoding complexity, we divide the continuous output $z$ into disjoint decision regions to construct a \gls{dmtmac}, where the transition probability from tag input combination $x_{m_{\mathcal{K}}}$ to detector output combination $\hat{x}_{m_{\mathcal{K}}'}$ is
		\begin{equation}
			P(\hat{x}_{m_{\mathcal{K}}'} \mid x_{m_{\mathcal{K}}}) = \int_{\mathcal{R}_{m_{\mathcal{K}}'}} f(z \mid \mathcal{H}_{m_{\mathcal{K}}}) \dd z,
			\label{eq:dmtmac}
		\end{equation}
		where $\mathcal{R}_{m_{\mathcal{K}}'}$ is the decision region over $z$ for hypothesis $\mathcal{H}_{m_{\mathcal{K}}'}$.
	\end{subsection}
